AdaptiveConformal: An `R` Package for Adaptive Conformal Inference

### 2023-11-30 paper.qmd
Fixed references

The FluSight challenge collected forecasts for multiple prediction targets. For this case study, we focus on national (US) one-week ahead forecasts of weighted influenza-like illness (wILI), which is a population-weighted percentage of doctors visits where patients presented with influenza-like symptoms [@biggerstaff2016flusight]. The FluSight dataset, which is publicy available, include forecasts derived from 21 different forecasting models, from both mechanistic and statistical viewpoints [@tushar2018flusightnetwork, @tushar2019flusight]. For our purposes, we treat the way the forecasts were produced as a black box.

>>>>

The FluSight challenge collected forecasts for multiple prediction targets. For this case study, we focus on national (US) one-week ahead forecasts of weighted influenza-like illness (wILI), which is a population-weighted percentage of doctors visits where patients presented with influenza-like symptoms [@biggerstaff2016flusight]. The FluSight dataset, which is publicy available, include forecasts derived from 21 different forecasting models, from both mechanistic and statistical viewpoints [@flusight2020;@tushar2018flusightnetwork;@tushar2019flusight]. For our purposes, we treat the way the forecasts were produced as a black box.
